Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-07-19 Thesis/chapter/03-theoretical-background.tex
cigs figure from Markvart Principles
theory overarbeitet

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Crystalline Silicon Photovoltaics}
\td{aka PV basics}
The vorgang of conversion of photons into voltaic energy can be broken down into two essential steps ( egal ob in silicon based or in plants): the creation of an electron hole pair and then their separation by the structure of the device. 
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction.
\td{stop}
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
\td{what is it? What is it used for? How does it work? What different kinds are there? }
\cite{markvart2013principles}
\td{CIGS has higher absorption coefficient because of direct band gap in contrast to crystalline silicon which has an indirect band gap and therefore less absorption probability.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CIGS}
CIGS ($\text{CuIn}_\text{x}\text{Ga}_{\text{(1-x)}}\text{Se}_2$) is of the chalcopyrite group (tetragonal crystal system) and can be used as thin film \gls{pv}. 
Just like CdTe, GaAs and amorphous silicon CIGS have much higher absorption coefficients 
(lower penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
These thin film \gls{pv}s not only use less material, but also can be used in flexible applications.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
wer penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}).

\subsubsection{Photovoltaics Basics}
The process of conversion of photons into voltaic energy can be broken down into two essential steps (both in silicon based \gls{pv} or in plants): 
the creation of an electron hole pair and then its separation by the structure of the device.\cite{markvart2013principles}
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction.
This is mainly achieved through a p-n junction.\td{cite a good source} 
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still have the biggest market share in the \gls{pv} segment including polycrystalline and monocrystalline silicon.
Together with amorphous silicon 2020 80\% of all sold \gls{pv} where made of silicon.
A comprehensive overview over different \gls{pv} technologies can be found in \cite{markvart2013principles}.
\td{What different kinds are there? }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{CIGS}
\gls{cigs} (\ch{CuIn_{x}Ga_{1-x}Se2}) is of the chalcopyrite (\ch{CuFeS2}) group (tetragonal crystal system). 
It was first synthesised in 1953 by Harry Hahn et al.\cite{hahn1953untersuchungen} 
and it's potential use as \gls{pv} material in combination with \ch{CdS} was first mentioned in 1974\cite{wagner1974cuinse2}.
Just like CdTe, GaAs and amorphous silicon CIGS has much higher absorption coefficients 
(lower penetration depth) of visible light than crystalline silicon (see table \ref{tab:cigs:alpha}). 
This is due to a direct band gap rather than an indirect band gap (like crystalline silicon). 
These thin film \gls{pv}s not only use less material, but also can be used in flexible applications.
